Fitness tracking reveals task-specific associations between memory, mental health, and exercise

### 2021-09-21 paper/main.tex
added some notes to the results section

\section*{Results}
\begin{itemize}
  \item exploratory analysis (correlations)
    \begin{itemize}
    \item Memory-memory
    \item fitness-fitness
    \item survey-survey
    \item (fitness + survey)-memory
    \end{itemize}
  \item predictive analysis (regressions)
    \begin{itemize}
    \item Predict memory performance on held-out task from other tasks
    \item Predict memory performance on each task using fitness data
      \item Predict memory performance on each task using survey data
      \end{itemize}
    \item Reverse correlations: look at recent changes versus baseline trends
      \begin{itemize}
      \item Fitness profile that predicts performance on each task (barplots + timelines)
      \item Fitness profile for each survey demographic (barplots + timelines)
        \begin{itemize}
          \item Select out mental health demographics (based on meds, stress levels)
          \end{itemize}
        \end{itemize}
  \end{itemize}

>>>>

\section*{Results}
\begin{itemize}
\item characterizing behaviors (potentially broken down by 3--4
  fitness-defined categories, like activity level quartile; may also
  want to have separate figures: one for characterizing behaviors on
  average, and a second breaking down by fitness variable, e.g. after
  the correlation analyses are presented)
  \begin{itemize}
  \item Free recall: pfr, lag-CRP, spc
    \item Naturalistic recall: reproduce a version of the sherlock
      movie/recall trajectories
    \item Foreign language flashcards: p(correct) by activity level
      \item Spatial learning: mean error by number of shapes
      \end{itemize}
    \item Fitness info (break down by task performance, potentiall
      separately for each task); also separate out recent (raw) and recent versus baseline
      \begin{itemize}
      \item activity (steps, zone minutes, floors/elevation)
      \item resting heart rate
        \item sleep
        \end{itemize}
  \item exploratory analysis (correlations)
    \begin{itemize}
    \item Memory-memory
    \item fitness-fitness
    \item survey-survey
    \item (fitness + survey)-memory
    \end{itemize}
  \item predictive analysis (regressions)
    \begin{itemize}
    \item Predict memory performance on held-out task from other tasks
    \item Predict memory performance on each task using fitness data
      \item Predict memory performance on each task using survey data
      \end{itemize}
    \item Reverse correlations: look at recent changes versus baseline trends
      \begin{itemize}
      \item Fitness profile that predicts performance on each task (barplots + timelines)
      \item Fitness profile for each survey demographic (barplots + timelines)
        \begin{itemize}
          \item Select out mental health demographics (based on meds, stress levels)
          \end{itemize}
        \end{itemize}
  \end{itemize}
